---
title: "lab2"
author: "Audrey Comer"
date: "2/5/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
choco <- read.csv("https://xdaiisu.github.io/ds202materials/hwlabs/choco.csv")
head(choco)
```
##How are ratings distributed? Draw a histogram of ratings and describe it. Don't forget to mention outliers, if there are any.
```{r}
library(ggplot2)
mean(choco$Rating)
hist(choco$Rating,col="brown",xlab="Rating", ylim=c(0,800), main="Histogram of Chocolate Ratings")
hist(choco$Rating,breaks=seq(0,5,by=.25),col="brown",xlab="Rating", main="Histogram of Chocolate Ratings")
```

Outliers are the ratings of 5 and 2 and below. The majority of the ratings are between 2.5 and 4. The mode is 3.5. The average (not found in the histogram) is 3.19.
```{r}
boxplot(choco$Rating)
```


##Do ratings depend on the cacao percentage of a chocolate bar?
```{r}
plot(choco$Cocoa.Pct,choco$Rating,xlab="Cacao Percent", ylab="Rating", main="Scatterplot of Rating by Cacao Percent")
```

There appears to be no correlation between cacao percentage and rating.
