---
title: "team"
author: "Audrey Comer"
date: "2/5/2019"
output: html_document
---

```{r}
choco <- read.csv("https://xdaiisu.github.io/ds202materials/hwlabs/choco.csv")
```

##1. What is the overall number of chocolate bars rated?
```{r}
nrow(choco)
```

##2. How does the number of ratings depend on the year? Draw a bar chart of the number of reports.

Based on the below barchart, the number of ratings increased with year until 2016.

```{r}
t <- table(choco$Review.Date)
head(t)
barplot(t)
```

##3. How do ratings compare across different company locations? Focus on the three locations with the most ratings.
###(Hint: They are U.S.A., France, and Canada, but find them out using codes.)

```{r}
countries <- choco$Company.Location #creates vector of countries
table(countries) #creates table with all countries and their rating frequency
sort(table(countries), decreasing = T) #sorts table by frequency
c2<-sort(table(countries), decreasing = T) #creates new variable to make calling headings simpler
head(c2,3) #calls top three countries and # of ratings
barplot(head(c2,3), ylab='Number of Ratings', ylim=c(0,800), width=1, col=c('blue', 'yellow','red'))
```

#Histograms of rating distribution in each of the top three countries
```{r}
usa <- choco[choco$Company.Location == "U.S.A.",]
fr <- choco[choco$Company.Location == "France",]
can <- choco[choco$Company.Location == "Canada",]
hist(usa$Rating, breaks=seq(1,5,by=0.25), ylim=c(0,200), col='blue', xlab='Rating', main='Ratings of American chocolate')
hist(fr$Rating, breaks=seq(1,5,by=0.25), ylim=c(0,40), col='yellow', xlab='Rating', main='Ratings of French chocolate')
hist(can$Rating, breaks=seq(1,5,by=0.25), ylim=c(0,30), col='red', xlab='Rating', main='Ratings of Canadian chocolate')
?hist
```



##4. Brainstorm and write down an interesting question that can be answer from the dataset. The question should not duplicate the questions above.

##5. Answer the question from the dataset.